### 2015-10-19 FS3/AD/ad_a1.tex
AD:W1-2:A1,take 1

	\item $n^2 \cdot \operatorname{log} n \in O(n^3) \Omega(n^2)$

@@

>>>>

	\item $n^2 \cdot \operatorname{log} n \in O(n^3) \cap \Omega(n^2)$

@@

\subsubsection{}
	3n^3-6n+20 \in O(n^3) \Leftrightarrow lim_{n\rightarrow\infty}\frac{3n^3-6n+20}{n^3} < \infty
	lim_{n\rightarrow\infty}\frac{3n^3-6n+20}{n^3} = lim_{n\rightarrow\infty} \frac{3n^3}{n^3}-\frac{6n}{n^3}+\frac{20}{n^3}=lim_{n\rightarrow\infty}3-\frac{6}{n^2}+\frac{20}{n^3}=3-0+0<\infty
	\Rightarrow 3n^3-6n+20 \in O(n^3)  ~~~~~~~~\square
\subsubsection{}
	n^2 \cdot \operatorname{log} n \in O(n^3) \cap \Omega(n^2) \Leftrightarrow lim_{n\rightarrow\infty} \frac{n^2 \cdot \operatorname{log} n}{n^3} < \infty \land lim_{n\rightarrow\infty} \frac{n^2 \cdot \operatorname{log} n}{n^2} > 0
	\frac{n^2 \cdot \operatorname{log} n}{n^2} = \frac{1 \cdot \operatorname{log} n}{1} = \operatorname{log} n > 0~ \forall n > 1 \Rightarrow n^2 \cdot \operatorname{log} n \in \Omega(n^2)
	lim_{n\rightarrow\infty} \frac{n^2 \cdot \operatorname{log} n}{n^3} = lim_{n\rightarrow\infty} \frac{\operatorname{log} n}{n} \overset{\text{l'H}}{=} lim_{n\rightarrow\infty}\frac{1}{n} \cdot \frac{1}{1} = lim_{n\rightarrow\infty} \frac{1}{n} = \frac{1}{\infty} = 0 \Rightarrow n^2\cdot\operatorname{log} n \in  O(n^3)
	\Rightarrow n^2 \cdot \operatorname{log} n \in O(n^3) \cap \Omega(n^2)~~~~\square
